Dissertation Manuscript

### 2024-06-26 Sections/full.qmd
turn on code show; switch default manuscript to html

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
page-layout: full
code-fold: true
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

>>>>

---
title: "The Role of Variability in Learning Generalization: A Computational Modeling Approach"
author:
- name: Thomas E. Gorman
  affiliations: 
  - name:  Department of Psychological and Brain Sciences, Indiana University-Bloomington, USA
    affiliation-url: https://psych.indiana.edu/
  - name:  Program in Cognitive Science, Indiana University-Bloomington, USA
    affiliation-url: https://cogs.indiana.edu/index.html
  url: https://tegorman13.github.io/
  email: tegorman@iu.edu
  orcid: "0000-0001-5366-5442"
page-layout: full
code-fold: show
code-tools: true
toc: true
toc-location: body
toc-depth: 4
cache: true
format-links: [hikmah-manuscript-pdf, gfm, docx]
execute: 
  warning: false
  eval: true
format:
  html: default
  hugo-md:
    echo: false
    include: true
    html-math-method: mathjax
    output-file: diss_full_hugo.md
  gfm:
    echo: false
    #output: false
    output-file: diss_full_gfm.md
  hikmah-manuscript-pdf:
    echo: false
    output-file: "tg_full_disser.pdf"
    mainfont: "Linux Libertine O"
    mainfontoptions:
      - "Numbers=Proportional"
      - "Numbers=OldStyle"
    mathfont: "Libertinus Math"
  docx:
    echo: false
    prefer-html: true
    output-file: "TG_Full_Dissert.docx"
    toc: true
prefer-html: true
---

### 2024-06-26 paper.qmd
turn on code show; switch default manuscript to html

<iframe src="/Manuscript/output/TG_Full_Dissertation.pdf" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
```

>>>>

<iframe src="/Manuscript/output/manuscript.html" frameborder="0" style="overflow:hidden;height:95%;width:100%;border:2px solid #ccc;" height="95%" width="100%" name="manuscript"></iframe>
```
